---
title: "Model Card: XGB Model for Goalkeepers"
date: '`r Sys.Date()`'
output: 
  html_document
params:
    board: !r pins::board_folder(here::here(paste0("season ","2024_25","/models")))
    name: xgb_gk_reg
    version: NULL
---

```{r setup, include=FALSE}
library(tidyverse)
library(vetiver)
library(pins)
library(yardstick)
knitr::opts_chunk$set(echo = FALSE)
v <- vetiver_pin_read(params$board, params$name, version = params$version)
v_meta <- pin_meta(params$board, params$name)
theme_set(theme_light())
```

A [model card](https://doi.org/10.1145/3287560.3287596) provides brief, transparent, responsible reporting for a trained machine learning model.

## Model details

- Developed by PRENOLAN MUNSAMY
- `r cli::pluralize("{v$description} using {ncol(v$prototype)} feature{?s}")`
- XGB regression model built to predict the total points each GOALKEEPERS will earn in each game week
- More details on feature engineering and/or data preprocessing for model
- Version `r v$metadata$version` of this model was published at `r v_meta$created`
- If you have questions about this model, please contact prenolanmunsamy@yahoo.com

## Metrics

- The metrics used to evaluate this model are rmse

## Training data & evaluation data

- The training dataset for this model was all game weeks data from the 2022_23 season
- The training dataset for this model has the "prototype" or signature:

    ```{r}
    glimpse(v$prototype)
    ```

- The validation dataset used in this model card is the first 18 game weeks of the 2023_24 season
- The test dataset used in this model card is the last 18 game weeks of the 2023_24 season

```{r}
## EVALUATION DATA:
# eval_data <- 
#   load_defender_data(here(paste0("season 2024_25","/data/model"),
#                           "model_data.csv"))

```


## Quantitative analyses {.tabset}

### Overall model performance

```{r}
v %>% 
  pluck("metadata","user","metrics") %>% 
  as_tibble()
```

### Visualize model performance

```{r, fig.height=3}
# preds %>%
#     ggplot(aes(price, .pred, color = type)) +
#     geom_abline(slope = 1, lty = 2, color = "gray60", size = 1.2) +
#     geom_point(alpha = 0.5, show.legend = FALSE) +
#     facet_wrap(vars(type))
```



